A systematic search for transiting planets in the \KT\ data

### 2015-02-14 ms.tex
results words

\Fig{completeness} shows the fraction of recovered signals as a function of
the physical parameters of the injection and the magnitude of the star.
As expected, the shallower transits at longer periods are recovered less
robustly.

@@

After running the 21XXX light curves through our full pipeline, we end up
with XXXX TCEs \dfmtodo{change this name} and after hand vetting, we are left
with YYYY convincing transiting candidates.
Of these candidates, ZZZ are probable binaries with obviously visible
secondary eclipses and we list these candidates in Table \dfmtodo{SOMETABLE}.
This leaves WWW planet candidates that are listed in Table
\dfmtodo{SOMETABLE}.

\paragraph{Posterior constraints on physical parameters}

To fit for the observable parameters of the transit signals in detail, we use
the same linear model for the systematics but then we combine this with a
physical transit model (M\&A, etc.).
Since this transit model is no longer linear, we use Markov Chain Monte Carlo
(MCMC; cite emcee) to draw posterior samples from this model.
At each step in the chain, we \emph{marginalize over the model of the
systematics}.
This means that we don't de-trend the data or make any hard decision about
the actual value of the systematics.
We sample the stellar density, limb-darkening coefficients, period, phase,
radius ratio, impact parameter, eccentricity, and argument of periapsis.
\dfmtodo{List priors.}
The quantiles of these posterior samplings are given in table \dfmtodo{some
table} and the full chains are available electronically \dfmtodo{some URL}.

@@

\acknowledgments
It is a pleasure to thank
Ruth Angus (Oxford), Tom Barclay (Ames), \etal
for helpful contributions to the ideas and code presented here.
DFM, DWH, and DW were partially supported by the National Science Foundation
(grant IIS-1124794),
the National Aeronautics and Space Administration
(grant NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.
BTM was supported by a National Science Foundation Graduate Research
Fellowship (grant DGE‐1144469).

This research made use of the NASA \project{Astrophysics Data System}.
This \paper\ includes data collected by the \kepler\ mission. Funding for the
\kepler\ mission is provided by the NASA Science Mission directorate.
These data were obtained from the Mikulski Archive for Space Telescopes
(MAST).
STScI is operated by the Association of Universities for Research in
Astronomy, Inc., under NASA contract NAS5-26555.
Support for MAST is provided by the NASA Office of Space Science via grant
NNX13AC07G and by other grants and contracts.

>>>>

\Fig{completeness} shows the fraction of recovered signals as a function of
the physical parameters of the injection and the magnitude of the star.
As expected, the shallower transits at longer periods are recovered less
robustly.
It is worth noting that this figure is a two-dimensional projection (or
marginalization) of a higher dimensional measurement.
For example, this completeness map is conditioned on our assumptions about
the eccentricity distribution of planets and it is marginalized over the
distribution of stellar parameters.
It is possible to relax this assumption and apply different distributions by
re-weighting the simulations used to generate this figure.
Therefore, alongside this \paper, we publish the full list of injection
simulations\footnote{SOMEURL} to be used for population inference (occurrence
rate measurements).
In \fig{completeness}, we also show the detection efficiency---marginalized
over the same range of periods---as a function of stellar magnitude in the
\kepler\ bandpass as reported in the EPIC.

@@

After running the 21XXX light curves through our full pipeline, we end up with
XXXX TCEs \dfmtodo{change this name} and after hand vetting by the two first
authors of this \paper, we are left with YYYY convincing transiting
candidates.
We choose to separate this list into two tables: planet candidates
(\tab{cand}) and eclipsing binary candidates (\tab{eb}).
For our purposes, we define an binary candidate as any system where we can
find a secondary eclipse by visual inspection but in most cases, the
secondary eclipse is also detected as a smaller transit signal at the same
period as the primary.
In this dataset, we discover ZZZ planet candidates around WWW stars.
Two of these were previously published \citep{Crossfield:2015} but, to our
knowledge, the remaining list is currently unpublished.
The third planet published by \citet{Crossfield:2015} is found as the third
signal for that target by our pipeline but it falls just below our
signal-to-noise cut so we left it out of the catalog for consistency.
This suggests that a less conservative cut in signal-to-noise and more
aggressive machine vetting could yield a much more complete catalog at smaller
radii and longer periods even with the existing dataset.

For the binaries, we simply list the period, phase, and depth determined by
the search algorithm but for the planet candidates, we perform a full physical
transit fit to the light curve.
To do this fit, we use Markov Chain Monte Carlo \citep[MCMC;][]{emcee} to
sample from the posterior probability for the stellar and planetary
parameters taking limb darkening and integration time into account.
In this fit, we continue to model the trends in the data as a linear
combination of 150 ELCs but, at this point, we combine this with a realistic
light curve model \citet{ma, kipping-ld}.
Even though we have no constraints on the stellar parameters, we also sample
over a large range in stellar mass and radius so that future measurements can
be applied by re-weighting the published samples.
In \tab{cand} we list the sample quantiles for the observable quantities and
the full chains are available electronically at \dfmtodo{some URL}.

SOMEFIGURE shows the distribution of radius ratios and periods of candidates
from our sample.

@@

\acknowledgments
It is a pleasure to thank
Andrew Vanderburg (Harvard),
Ruth Angus (Oxford), Tom Barclay (Ames), \etal
for helpful contributions to the ideas and code presented here.
DFM, DWH, and DW were partially supported by the National Science Foundation
(grant IIS-1124794),
the National Aeronautics and Space Administration
(grant NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.
BTM was supported by a National Science Foundation Graduate Research
Fellowship (grant DGE‐1144469).

This research made use of the NASA \project{Astrophysics Data System} and the
NASA Exoplanet Archive.
The Archive is operated by the California Institute of Technology, under
contract with NASA under the Exoplanet Exploration Program.
This \paper\ includes data collected by the \kepler\ mission. Funding for the
\kepler\ mission is provided by the NASA Science Mission directorate.
These data were obtained from the Mikulski Archive for Space Telescopes
(MAST).
STScI is operated by the Association of Universities for Research in
Astronomy, Inc., under NASA contract NAS5-26555.
Support for MAST is provided by the NASA Office of Space Science via grant
NNX13AC07G and by other grants and contracts.
